\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[latin1]{inputenc}
\usepackage{a4wide}
\usepackage[dvips]{graphicx}
\usepackage{float}

\usepackage[
pdfauthor={},
pdftitle={},
pdfcreator={pdftex},
]{hyperref}

\include{ace}

\begin{document}
\setlength{\parindent}{0pt}

\include{titlepage}
\newpage

\tableofcontents
\newpage

\listoftables
\listoffigures
\newpage


\section{Introduction}
\ace will need a network layer that provides the following two basic features:

\begin{itemize}
 \item discovery
 \item communication
\end{itemize}

Let us explain these two basic points in greater detail.

\subsection{Discovery}
In \ace a user will be able to share a document so others can join him editing this document. Without a way of discovering other shared documents, the application is pretty useless. The discovery should be as simple as possible. There are several technologies that allow automatic discovery of services, for instance \emph{Jini}, \emph{Bonjour} (also known as zero-conf networking) and diverse peer-to-peer frameworks.

\subsection{Communication}
This is the basic requirement. Without some form of communication collaboration is infeasible. There are different technologies ranging from plain socket communication over remote method invocation to complex peer-to-peer frameworks.

\subsection{Network Basics}
The basic operations a user will perform on a document are:
\begin{itemize}
 \item publish a document
 \item unpublish a document
 \item join an editing session
 \item leave an editing session
\end{itemize}

\subsection{Overview}
In the following sections we introduce several network technologies that could be interesting for the implementation of \ace. 

\begin{itemize}
 \item \emph{JGroups}
 \item \emph{Rendezvous/Bonjour}
 \item \emph{Jini}
 \item \emph{JXTA}
 \item \emph{BEEP}
\end{itemize}


\input{tech/jgroups.tex}
\input{tech/rendezvous.tex}
\input{tech/jini.tex}
\input{tech/jxta.tex}
\input{tech/beep.tex}


\end{document}
