\chapter{Funtionality}
\label{chapter:functionality}

The goal of the project ACE is to create a plattform independent collaborative text editor. To achieve that goal the editor must satisfy basic text editor functionality as well as collaborative editor functionality.\\

A basic text editor must have features like create new, load and save documents. Further it would be userfriendly to have multiple documents open at the same time and switch between them. Operations like cut/copy/paste and undo/redo shouldnt be missing. A more detailed description of the goals can be found in the \textit{System Requirement: 2.1 Mandatory Goals}. See section \ref{sect:algorithm.undoredo} for a description about the lack of undo/redo in our editor.\\

Besides the basic text editor functions, a collaborative text editor must support the publication of documents. Published documents should be discovered automatically by all other users running a collaborative text editor in the same network. They can join the editing session for a published document or can be invited by its owner (publisher). All participants of such a session can read, write and delete the content of the corresponding document. To counteract misbehaviour the publisher can kick invited users which results in a blacklist entry until they receive a re-invite. To [MONSTER WORD INSERTED BY RASSS] each participant has his own color which is used to highlight the written text and draw the current cursor position (or selection).\\

Based on these facts we defined mandatory, optional and non-goals for our diploma work in \textit{System Requirements: Project Goals}. A description of the preview work can be found in \ref{sect:overview.previewwork}.
