\chapter{Lessons Learned}
\label{chapter:lessonslearned}



\section{General}
When we decided which technology to use to implement the network layer, we did
not have a complex prototype based on the chosen technology. \emph{Bonjour}
itself proved to be a good choice, however the \emph{Beepcore} Java library had 
some bugs that caused serious problems in the implementation. We could have
avoided that situation by implementing a prototype that would have used
the framework in a similar manner as ACE. Thus, we learned that it is
always a good idea to make some thorough tests before using a framework
in a project.



\section{Mark Bigler}
First of all, it was a great time with a really cool and efficient team. I have got to know new frameworks like \textit{GlazedLists} and \textit{Springframework} which are very usefull for GUI programming.

Writing all documents in English was a good practise to improve my english skills which are a bit more fluent now.

Too bad, we did not have twice as much time to realize even more features to make ACE a more powerful tool.
\subsection{Positive Points}
\begin{itemize}
\item great time and experience
\item new frameworks useful for GUI programming
\end{itemize}

\subsection{Negative Points}
\begin{itemize}
\item Not enough time to make a ".." project.
\end{itemize}



\section{Simon Raess}
The whole project ACE was a great success. We started from basically knowing
nothing about the topic to a working application. Although there are still
some open issues, we achieved the goals set at the beginning. 

When I look back I see one thing we should have done from the beginning:
writing a simulated implementation of the network layer. This would have
simplified testing of the two upper layers greatly. Testing network code is inherently non-deterministic. With the clear layering of the application 
we could have easily written an alternative (simulated) implementation of
the network layer to simplify testing inside a sandbox-like environment (i.e.
without access to the real network).

\subsection{Positive Points}
\begin{itemize}
 \item we achieved all mandatory and some optional goals we defined at the beginning of the diploma project in the amount of time we had
 \item through a clear separation of the layers we could work efficiently and independently
\end{itemize}

\subsection{Negative Points}
\begin{itemize}
 \item we did not implement a network simulator, which would have simplified testing greatly
 \item we did not investigate the used network technologies thoroughly enough
\end{itemize}



\section{Lukas Zbinden}
Intro...
\subsection{Positive Points}
\begin{itemize}
\item ...
\end{itemize}

\subsection{Negative Points}
\begin{itemize}
\item ...
\end{itemize}

