\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[latin1]{inputenc}
\usepackage{a4wide}
\usepackage[dvips]{graphicx}
\usepackage{float}

\usepackage[
pdfauthor={ace project team},
pdftitle={Final Report},
pdfcreator={pdftex},
]{hyperref}

\include{ace}

\begin{document}
\setlength{\parindent}{0pt}

\include{titlepage}
\newpage

\tableofcontents
\newpage

\listoftables
\listoffigures
\newpage


\section{Introduction}
The purpose of this document is to give a general overview of all the available documents, 

\subsection{Referenced Documents}
All the referenced documents can be found on the project website (\href{http://ace.iserver.ch/}{http://ace.iserver.ch}) or in the subversion repository.
\begin{itemize}
 \item PM Documents
 \begin{itemize}
  \item Projekthandbuch
  \item Projektplan
  \item Erfahrungsbericht
 \end{itemize}
 \item Other Documents
 \begin{itemize}
  \item Report Evaluation Algorithm
  \item Report Implementation Algorithm
  \item Report Evaluation Network
  \item Report Evaluation GUI
 \end{itemize}
\end{itemize}


\section{Project}
The planned project structure is described in the project plan and project manual.

\subsection{Steps}
The project was split into three distinct phases: initialization, construction, and termination. The construction phase was split into three subprojects: algorithm, network, and GUI.

\subsection{Results}
The expected results are described in the project plan. 

\subsubsection{Algorithm}
\paragraph{Report Evaluation Algorithm:} 
This report describes the core principles of collaborative editing, evaluates several algorithms and proposes a few for a possible implementation.

\paragraph{Report Implementation Algorithm:} 
This report describes which algorithm we chose in great detail. Also a justification for our selection is given.

\paraggraph{Report Implementation Testframework:}
This report describes the testframework and shows how one can define testcases (so called scenarios) for the testframework.

\subsubsection{Network}
\paragraph{Report Evaluation Network:}
This report describes the requirements a network layer of \ace must fulfill. It further describes some avaible network technologies and explains whether they are suitable. A set of selection criteria is given at the end of this report.

\subsubsection{GUI}
\paragraph{Report Evaluation GUI:}
The evaluation report GUI describes several key problems that must be solved in the graphical user interface of \ace.


\section{Status}
The goals as described in the project manual are all achieved. However, the implementation of undo in the algorithm still has some situation where it fails. We have a complete understanding how to solve these problems. The solution is not yet implemented.

See the \emph{report implementation algorithm} for a description of the remaining issues in the implementation of the user undo/redo.


\section{Outlook}
We achieved the main objectives of the semester project. We have built a good and solid foundation for a collaborative application. Now, we would like to make a brief outlook for the time up to the diploma project and also for the diploma project itself.

\subsection{Summer}
\begin{itemize}
 \item complete implementation of algorithm (undo/redo)
 \item selection of network technology
 \item GUI: integrated in existing application or standalone application?
\end{itemize}

\subsection{Diploma Project}
The implementation of a collaborative text editor will be the main goal of the diploma project. This goal includes several other goals that are needed for a fully functioning application.
\begin{itemize}
 \item network layer (discovery of available shared documents, communication)
 \item GUI: integration of algorithm, sharing of documents, discovery of shared documents
\end{itemize}

\end{document}
