\chapter{References}
\label{chapter:references}

This chapter lists the articles, books, as well as websites we used when
implementing ACE. Check the bibliography for references to technical
publications.


\section{Semester Project}
The documentation of the semester project is referenced throughout the
diploma project documentation. The most important parts about the 
semester project documentation have been added to this document. However,
for details the interested reader is referred to the semester project
documentation.

\begin{description}
 \item[Report Evaluation Algorithm] Report that describes the basic concepts of operational transformation as well as the evaluation of several operational transformation algorithms.
 \item[Report Implementation Algorithm] Report that contains information how the algorithm has been implemented. Most information in this document is no longer up-to-date, as quite some changes happened around the algorithm. Nonetheless, some interesting pieces can still be found in it.
 \item[Report Testframework] Describes the test framework implementation and how to use it.
 \item[Report Evaluation Network] Evaluation of several possible network technologies for the network layer implementation of ACE.
 \item[Report Evaluation GUI] Research in the area of the GUI and possible features in the graphical user interface.
\end{description}



\section{Websites}

\begin{description}
% \item[] \href{}{}
 \item[Spring Framework] \href{http://www.springframework.org/documentation}{http://www.springframework.org/documentation}
 \item[Glazed Lists] \href{http://www.publicobject.com/glazedlists/}{http://www.publicobject.com/glazedlists/}
 \item[jMock] \href{http://www.jmock.org/}{http://www.jmock.org/}
 \item[EasyMock] \href{http://www.easymock.org/}{http://www.easymock.org/}
 \item[AOP Alliance] \href{http://aopalliance.sourceforge.net/}{http://aopalliance.sourceforge.net/}
  \item[BEEP Core RFC 3080] \href{http://www.faqs.org/rfcs/rfc3080.html}{http://www.faqs.org/rfcs/rfc3080.html}
 \item[BEEP Overview] \href{http://www.cisco.com/en/US/about/ac123/ac147/ac174/ac179/about_cisco_ipj_archive_article09186a00800e55d5.html}{http://www.cisco.com/en/US/about/ac123/ac147/ac174/ac179/about_cisco_ipj_archive_article09186a00800e55d5.html}
 \item[BEEPCore.org] \href{http://www.beepcore.org/}{http://www.beepcore.org/}
 \item[Java BEEP Core] \href{http://sourceforge.net/projects/beepcore-java}{http://sourceforge.net/projects/beepcore-java}
 \item[BEEP Core Mailing List] \href{beepcore-java-users-admin@lists.sourceforge.net}{beepcore-java-users-admin@lists.sourceforge.net}
 \item[Bonjour] \href{http://www.apple.com/macosx/features/bonjour/}{http://www.apple.com/macosx/features/bonjour/}
 \item[Bonjour Developer] \href{http://developer.apple.com/networking/bonjour/index.html}{http://developer.apple.com/networking/bonjour/index.html}
 \item[Bonjour Javadoc] \href{http://developer.apple.com/documentation/Java/Reference/DNSServiceDiscovery_JavaRef/index.html}{http://developer.apple.com/documentation/Java/Reference/DNSServiceDiscovery_JavaRef/index.html}
 \item[nameser.h] \href{http://www.opensource.apple.com/darwinsource/10.3.8/tcpdump-9/tcpdump/nameser.h}{http://www.opensource.apple.com/darwinsource/10.3.8/tcpdump-9/tcpdump/nameser.h} 
 \item[DNS-SD Draft] \href{http://files.dns-sd.org/draft-cheshire-dnsext-dns-sd.txt}{http://files.dns-sd.org/draft-cheshire-dnsext-dns-sd.txt}
 \item[mDNSResponder] \href{http://developer.apple.com/documentation/Darwin/Reference/ManPages/man8/mDNSResponder.8.html}{http://developer.apple.com/documentation/Darwin/Reference/ManPages/man8/mDNSResponder.8.html}
\item[Bonjour Mailing List] \href{bonjour-dev@lists.apple.com}{bonjour-dev@lists.apple.com}   
 \item[Apache ASN.1 Subproject] \href{http://directory.apache.org/subprojects/asn1/}{http://directory.apache.org/subprojects/asn1/}
 \item[JAXP + SAX for XML] \href{http://www.javazoom.net/services/newsletter/xmlgeneration.html}{http://www.javazoom.net/services/newsletter/xmlgeneration.html}
 \item[JAXP + SAX for XML 2] \href{http://www.javaworld.com/javaworld/jw-08-2000/jw-0804-sax.html}{http://www.javaworld.com/javaworld/jw-08-2000/jw-0804-sax.html}
\end{description}


\section{Books}
\begin{description}
 \item[Design Patterns] Elements of Reusable Object-Oriented Software. By Erich Gamma, Richard Helm, Ralph Johnson, John Vlissides.
\end{description}
